---
title: "OpenCLeaR"
author: "AG"
date: "2026-07-30"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OpenCLear Overview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# OpenCLeaR Paket-Quellcode

Dieses Dokument fasst die wichtigsten Dateien des Pakets zusammen.

## R-Code und Konfiguration

### DESCRIPTION
```{r, code=readLines('../DESCRIPTION'), eval=FALSE, echo=TRUE}
```

### R/OpenCLeaR-package.R (initialization etc)
```{r, code=readLines('../R/OpenCLeaR-package.R', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

### R/debug.R (debug etc)
```{r, code=readLines('../R/debug.R', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

### R/print.R (print Methoden)
```{r, code=readLines('../R/print.R', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```
### src/RcppInterface.cpp (some declarations)
```{r, code=readLines('../src/RcppInterface.cpp', warn=FALSE), eval=FALSE, echo=TRUE, comment="", class.source="cpp"}
```

## Build-System (Makevars)

autmated tasks, generate src/RcppExport.cpp, NAMESPACE and Rd files:

### Makefile
```{r, code=readLines('../Makefile', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

Unix style

### src/Makevars
```{r, code=readLines('../src/Makevars', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

Windows

### src/Makevars.win
```{r, code=readLines('../src/Makevars.win', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

## CMake Konfiguration

add all third-party code via git:

### src/backend/CMakeLists.txt
```{r, code=readLines('../src/backend/CMakeLists.txt', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```

get compiler configuration:

### src/backend/cmake/find_toolchain.cmake
```{r, code=readLines('../src/backend/cmake/find_toolchain.cmake', warn=FALSE), eval=FALSE, echo=TRUE, comment=""}
```


## Rcpp Interface to OpenCL kernels
nur rnorm als Bsp.

### src/rnormCL.cpp
```{r, code=readLines('../src/rnormCL.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### R/rnormCL.R
```{r, code=readLines('../R/rnormCL.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```

## C++ Backend

### src/backend/src/internal/CLpp.hpp
```{r, code=readLines('../src/backend/src/internal/CLpp.hpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### src/backend/src/CLpp.cpp
```{r, code=readLines('../src/backend/src/CLpp.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### src/backend/src/init.cpp
```{r, code=readLines('../src/backend/src/init.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### src/backend/include/backend/init.hpp
```{r, code=readLines('../src/backend/include/backend/init.hpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### src/backend/include/backend/export.hpp
```{r, code=readLines('../src/backend/include/backend/export.hpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

Backend interface to OpenCL kernel

### src/backend/src/rnormcl.cpp
```{r, code=readLines('../src/backend/src/rnormcl.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

### src/backend/include/backend/rnorm.hpp
```{r, code=readLines('../src/backend/include/backend/rnormcl.hpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

Kernel library

### src/backend/kernel/libkernel.cpp
```{r, code=readLines('../src/backend/kernel/libkernel.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="cpp", comment=""}
```

Finally a real OpenCL kernel

### src/backend/kernel/rnorm.cl
```{r, code=readLines('../src/backend/kernel/rnorm.cl', warn=FALSE), eval=FALSE, echo=TRUE, class.source="c", comment=""}
```


## inline Interface

plugin definition

### R/inline.R
```{r, code=readLines('../R/inline.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```

example

### inst/examples/rnormCLinline.R
```{r, code=readLines('../inst/examples/rnormCLinline.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```

### inst/examples/parallel_mh.R
```{r, code=readLines('../inst/examples/parallel_mh.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```

### inst/examples/parallel_mh_generic.R
```{r, code=readLines('../inst/examples/parallel_mh_generic.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```
examples in Rd files>

### man/generateInlineCL.Rd
```{r, code=readLines('../man/generateInlineCL.Rd', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}

```

### man/makeAdaptiveCL.Rd
```{r, code=readLines('../man/makeAdaptiveCL.Rd', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}

```

### kernel/idw_kernel.cl
```{r, code=readLines('../inst/kernel/idw_kernel.cl', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}

```

### interface/idw_rcpp.cpp
```{r, code=readLines('../inst/interface/idw_rcpp.cpp', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}

```
## Tests

configuration

### tests/testthat.R
```{r, code=readLines('../tests/testthat.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```

finally a test

### tests/testthat/test-rnormCL.R
```{r, code=readLines('../tests/testthat/test-rnormCL.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```


An **inline** call could look like this:

source(paste(system.file("inst/examples", package = "OpenCLeaR"),"rnormCLinline.R",sep="/"))

using 
### inst/examples/rnormCLinline.R
```{r, code=readLines('../inst/examples/rnormCLinline.R', warn=FALSE), eval=FALSE, echo=TRUE, class.source="r", comment=""}
```
